### 2016-10-28 ms/ms.tex
misc

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for system-level
  conservation biology. Using a long-term data set comprising nearly
  20,000 pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing assembly to be punctuated
  by significant reorganizations of interactions. In contrast, the
  non-assembling networks did not restructure as frequently. Across
  all communities, Pollinator species were opportunistic in the
  flowers they visited. Indeed, the most persistent and generalized
  species were also the most variable in their network positions. High
  species and interaction turnover was ubiquitous across assembling
  and non-assembling communities, though unique interactions turnover
  at higher rates in assembling hedgerows as the networks continually
  reorganize. Nestedness of assembling networks also increased through
  time, but there was no increase in robustness to simulated plant
  extinctions. Our results elucidate some of the mechanisms underlying
  plant-pollinator network assembly and restoration, while providing
  further evidence that hedgerows are a valuable tool for promoting
  species conservation and ecosystem provision in agricultural areas.
\end{abstract}

@@

%% there are other ways to assemble that are not preferentia;
%% attchment, particularly vis big reorganizations of interactions
%% Lauren I love this paragraph!
In contrast to the ordered network build-up described by preferential
attachment, significant reorganizations of interactions can punctuate
assembly \citep{peel2014detecting}. Such significant reorganizations
of interactions, or network changing points, are observed in social
networks responding to abrupt shifts in the behavior of interactors
\citep{peel2014detecting}. In ecological communities, such shifts may
occur if, as new species colonize, resident species change their
interaction partners to optimize their foraging effort. In
plant-pollinator communities, theory predicts pollinators optimize
their use of floral resources to reduce interspecific competition and
improve resource-use efficiency \citep{pyke1984optimal,
  valdovinos2010consequences, valdovinos2013adaptive,
  albrecht2010plant, Bluthgen2007}. No studies, however, have examined
whether changing points occur during ecological network assembly, and
how these changes relate to the species behavior.

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially 'applied succession'
\citep[e.g.,][]{parker1997scale}. In pollination systems, the time
since an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, forup2008restoration,
  devoto2012understanding}, suggesting interactions are changing as
the community develops. Understanding the mechanisms of network
assembly will help to guide community restoration. Facilitating
network restoration is especially imperative in areas where species
interactions provide essential ecosystem services, such as crop
pollination. In intensively managed agricultural landscapes, the
demand for pollination services is the greatest
\citep{kremen-2008-10}. However, honey bees, managed extensively
around the world to provide crop pollination, are in global decline
\citep{neumann-2010-1, van-engelsdorp-2009-e6481}. In addition, native
pollinators, which are capable of providing sufficient crop
pollination \citep{kremen-2002-16816, winfree-2007-1105,
  kremen-2004-1109}, are in short supply because these landscapes make
poor habitats for pollinator populations \citep{kremen-2002-16816}. To
ensure the continued provision of ecosystem services and curb
biodiversity loss, it is critical to restore pollinators and their
interactions in agricultural landscapes. To promote pollinator
services in agriculture, farmers may chose to plant strips of native
plants along farm edges (hedgerows) to help provide habitat for
pollinators without removing arable land from production. Hedgerows
augment the richness, abundance and trait diversity of pollinators in
agricultural landscapes \citep{morandin-2013-829, mgonigle-2015-x,
  kremen-2015-602, ponisio2015farm}. In addition, hedgerows promote
the persistence and colonization of floral resource specialists
\citep{mgonigle-2015-x}. Little is known, however, about how new
species are being incorporated into the network as the community
assembles, or the consequences for interaction patterns and
robustness.

%% Lauren I would put 10 year dataset; and I *loved* the way you
%% organized the ideas here!!
We explore the process of network development using a nine year
dataset of plant-pollinator communities assembly following hedgerow
restoration in the highly simplified and intensively managed
agricultural landscape of California's Central Valley.  We first
determine whether the mechanism underlying network assembly is a build
up of interactions as would be predicted by preferential attachment,
or punctuated by significant reorganizations of interactions (i.e.,
network changing points). Even with changing points in interaction
organization, networks could still be assembling via preferential
attachment if the network reorganizations were primarily driven the by
peripheral, temporally variable species while a stable, well-connected
core of species persist. We test whether the species that are most
variable in their network position --- and thus important contributors
to network reorganizations --- are less persistent and connected
species. To further explore the mechanisms underlying the temporal
dynamics of the networks, we examine patterns in the species and
interaction temporal turnover. Lastly, we investigate whether networks
are assembling toward predictable interaction patterns, and the
ramifications for the robustness of the networks to species
extinction.

@@

We surveyed plant-pollinator interaction networks of independent
assembling hedgerows communities (N=5), as well as in two types of
non-assembling communities to serve as controls: unrestored, weedy
field margins (N=19) and mature hedgerows (greater than 10 years since
planting, N=29). The sites were located in the Central Valley of
California in Yolo, Colusa and Solano Counties. This area is composed
of intensively managed agriculture --- primarily monocultures of
conventional row crops, vineyards and orchards. Hedgerows we planted
along field margins where they do not remove valuable land from
production. Plantings are between are ca.~3--6 m wide and
approximately 350 m long, bordering large (ca.\ 30--hectare) crop
fields. Hedgerows consist of native, perennial, shrub and tree
plantings including \textit{Rosa californica}, \textit{Cercis
  occidentalis}, \textit{Ceanothus spp.}, \textit{Heteromeles
  arbutifolia}, \textit{Sambucus mexicana}, \textit{Eriogonum spp.},
\textit{Baccharis spp.}, \textit{Salvia spp}. and others
\citep{kremen-2015-602, mgonigle-2015-x}. The mean distance between
monitoring sites was 15 km, and the minimum distance between sites of
the same type sampled in the same year was 2 km.  The entire area
surveyed spanned almost 300 km$^2$. The crop fields adjacent to all
sites were similarly managed as intensive, high-input monoculture.

@@

We calculate species persistence as the proportion of surveys in which
a plant or pollinator is observed. Species observed consistently
within and between years are thus maximally persistent. Weighted
species degree is calculated from interaction observations from an
extensive dataset from Yolo County (approx.~18000 interaction records)
that included both the data included in this study and additional data
from sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness centrality \citep{freeman1978centrality} at each
site through time. Closeness centrality describes the centrality of a
species in the network by calculating path lengths to other vertices
(species) in the graph \citep{freeman1978centrality}. We use linear
mixed models to test whether the species closeness variability (log)
is related to the persistence or degree of that species \citep{lme4,
  lmetest}. We included random effects for species, as well as
site. Because the degree and persistence of pollinators were strongly
correlated, ($\rho = 0.84$, $p$-value $<$ $2*10^{-16}$), we include
each explanatory variable in the model separately. Plant degree and
persistence were not significantly correlated, but we use the same
models as we did for the pollinators for consistency. An approximately
logarithmic increase in closeness centrality, as would be expected
with assembly by preferential attachment, would also lead to a high
variability in closeness scores, so we test whether log closeness
centrality increases through time.

@@

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, ocupying the same network position and interacting with
similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species
(Fig.~S1). We develop a method to examine the temporal turnover of
interactions with weightings based on their similarity. We followed
\cite{ahn2010link} algorithm to hierarchically cluster all the
interactions (edges) across sites and years based on their similarity,
and build a dendrogram. The interaction similarity is based how may
plants and pollinators (vertices) two edges share \citep{ahn2010link,
  kalinka2011linkcomm}. The more species edges shared in common, the
shorter the branch length between them on the dendrogram.  We next
calculated the temporal turnover of interactions weighted by their
similarity, as approximated by ``phylogenetic'' distance
\citep{graham2008phylogenetic, picante-2010-1463}. When then use
linear models to test whether the weighted turnover of interactions
varied between assembling and non-assembling networks \citep{lme4,
  lmetest}.

@@

To evaluate network nestedness, we used the estimator weighted NODF
\citep{nodf}. NODF evaluates whether species with fewer partners
interact with subsets of partners with which more connected species
interact \citep{nodf}. To estimate modularity, we use a hierarchical
clustering algorithm \citep{Newman2004, igraph}.  We calculated
standardized $z$-scores so that nestedness and modularity metrics
could be compared across communities. The $z$-scores were calculated
by generating an ensemble of $999$ randomly assembled communities,
subtracting the mean of the statistic calculated across these
communities from the observed value, and then dividing by the standard
deviation. To assemble random communities, we reshuffled the
interactions between species but fixed the total number of
interactions, species and interaction frequency distributions
\citep{Galeano2009}. We evaluate network specialization with the
metric H2, which estimates the deviation of the observed interaction
frequency between plants and pollinators from a null expectation where
all partners interact in proportion to their abundances
\citep{bluthgen-2006-9}. It ranges from zero for generalized networks
to one for specialized networks.

@@

\subsection*{Network robustness}
Lastly, we test whether the changes in interaction patterns associated
with network assembly affect the robustness of the network to species
loss. Following \cite{Memmott2004}, we simulate plant species
extinction and the subsequent extinction cascades of pollinator
species. Because the reproduction of plant species if facilitated by
active restoration efforts, it is unlikely the extinction of
pollinator species would affect plant populations in the
hedgerows. However, plants ceasing to bloom, for example in response
to drought, will likely affect the pollinators that depend on them. We
eliminate plants species based on their degree or abundance, and then
calculate the number of pollinators that secondarily went extinct. The
area below the extinction curve is an estimate of network robustness
\citep{Memmott2004, bipartite}.

% We also explored how the robustness to cascading perturbations changed
% as community assembled, using algebraic connectivity --- the second
% smallest eigenvalue of the Laplacian matrix
% \citep{fiedler1973algebraic} --- as a proxy for network robustness
% (Gaiarsa et al., submitted). Algebraic connectivity relates to how
% difficult it is to turn a network into completely disconnected groups
% of species \citep{costa2007characterization}. The larger the algebraic
% connectivity, the more robust a network is to cascading perturbations,
% and the harder it is to break the community into isolated groups of
% species (Gaiarsa et al., submitted).

@@

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
Network nestedness significantly increased with assembly
(Fig.~\ref{fig:baci}, estimate of the slope of nestedness through time
$\pm$ SE, $1.834 \pm 0.6142$, $p$-value=$0.022$). Modularity decreased
(Fig.~\ref{fig:baci}), though the slope was not significantly
different from zero (estimate of the slope of modularity through time
$\pm$ standard error of the estimate, $-0.524$ $\pm$ $0.295$,
$p$-value=$0.124$). In addition, none of the networks were
significantly modular ($z$-scores $<$ 2, Fig.~\ref{fig:baci})
Connectance decreased as the community assembled (Fig.~\ref{fig:baci},
estimate of the slope of connectance through time $\pm$ standard error
of the estimate, $-0.0434$ $\pm$ $0.0152$, $p$-value=$0.03$). In
contrast, specialization remained constant (estimate of the slope of
specialization through time $\pm$ SE, $0.003$ $\pm$ $0.015$,
$p$-value=$0.827$).

Both plant and pollinator species richness increased through time
(Fig.~\ref{fig:baci}, estimate of the slope of richness through time
$\pm$ SE, pollinators: $0.193$ $\pm$
$0.0729$, $p$-value=$0.008$; plants: $0.212$ $\pm$ $0.0653$,
$p$-value=$0.001$). Unsurprisingly, pollinator species are colonizing
and persisting at the assembling hedgerows. Plant species richness is
based on the flowers bbeing visiting by pollinators and not the
presence of a particular plant species at a site. Thus, though some
new plant species may establish themselves in the hedgerows, the
increase in plant richness in the networks is likely due to plants
attracting visitors, as they offer better rewards.

\subsection*{Network robustness}
Assembly did not effect the robustness of the networks to species
extinction when species where removed incrementally by degree
(estimate of the slope of robustness through time $\pm$ SE, $6*10^{-5}
\pm 4*10^{-3}$, $p$-value=$0.987$) or abundance ($0.001 \pm 0.003$,
$p$-value=$0.65$). % In contrast, the robustness of
% networks to cascading perturbations, as measured by the algebraic
% connectivity of the network, increased as the network assembled
% (Fig.~\ref{fig:rob}, estimate of the slope of robustness to cascading
% perturbations through time $\pm$ SE, $0.6814 \pm 0.272$,
% $p$-value=$0.042$).

@@

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations, the so called changing
points. If these network reorganizations were a product of
environmental forces alone, we would explect to observe the same
changing points at the same periods, consistently across all
sites. However, network changing points in non-assembling communities
are less frequent, and there are few consistent trends in when change
points occurred across all sites. Several sites had network changing
points between years 2009 and 2011 (Fig.~\ref{fig:changePoints}). In
California, 2011 marked the beginning of a multi-year drought. The
assembling hedgerows were not sampled in 2010, so disentangling
whether the changing points are due to skipping a year of assembly or
the drought is not possible. Interestingly, most assembling hedgerows
did not undergo a significant interaction reorganization immediately
after a hedgerow was planted (i.e., the transition from weedy field
margin to hedgerow). This result is consistent with the finding that
in our study system, hedgerow restoration takes several years to have
an impact on the plant-pollinator communities (Kremen and M'Gonigle,
in prep).

In addition to finding multiple network organization changing points
during assembly, the way in which these reorganizations occur was
different from what is expected by preferential attachment. Based on a
preferential attachment process, we expect that the most persistent
and high degree species would remain stable in the network core during
assembly \citep{barabasi1999emergence}. Surprisingly, however, we
encountered the opposite pattern. For example, the four most
ubiquitous species in our study landscape --- \textit{Halictus
  ligatus}, \textit{Halictus tripartitus}, \textit{Lasioglossum
  (Dialictus) incompletum}, and \textit{Toxomerus marginatus} --- were
the only species that changed which module they were a member across
years in all the assembling hedgerows. Because species degree and
persistence were strongly correlated, it is difficult to disentangle
the causal mechanism for why species with those characteristics are so
variable in their network position. Generalized species may be able to
better exploit the limited floral resources in the intensively managed
agriculture landscape, and thus also be the most persistent \citep[in
ant-plant mutualisms, ][]{diaz2010changes}. More persistent species
usually have longer phenologies, so they can visit many different
flowers, resulting in a higher degree \citep{Vazquez2009}. Either way,
our result suggests that adaptable species can change their network
position to utilize the most advantageous floral resources available,
which may depend on the other pollinator species that are present, and
the state of the plant community \citep{macleod2016measuring,
  gomez2006ecological, waser1996generalization}. Thus given the
opportunity and ability to use different resources, species will often
change their network positions \citep{macleod2016measuring}.

@@

The changes in network patterns with assembly also increased the
robustness of the networks to cascading perturbations -- providing
further evidence that hedgerows are a valuable tool for promoting
species conservation and ecosystem provision in agricultural areas
\citep{mgonigle-2015-x, ponisio2015farm, kremen-2015-602}. Because
network vulnerability to cascading perturbations, as measured by
algebraic connectivity, is correlated with species richness, the
increase and plant and pollinator richness following restoration is at
least partially responsible for enhancing network robustness to
cascading effects. The relationship between diversity and stability in
networks has been the subject of considerable debate
\citep[e.g.,][]{may1972will, pimm1984complexity,
  montoya2006ecological}. Our results provide one of the few empirical
examples of how restoring species diversity contributes to enhancing
network stability. Though these hedgerows were designed to promote
floral resources across the growing season and not specifically to
promote any specific network properties \citep{menz-2010-4}, the
pollinators assembled into resilient interaction patterns. With prior
knowledge of the floral preferences of pollinators, future restoration
efforts may also be able to incorporate promoting network stability
into planning efforts \citep{mgonigle2016tool}

Interestingly, however, the robustness of hedgerow communities to
species loss did not change with assembly. This is particularly
surprising given the observed increase in nestedness, which is often
associated with an enhanced in robustness to extinction
\citep{Memmott2004}. Perhaps assembling hedgerows have yet to reach
sufficient levels of nestedness to realize the benefits nestedness
confers. Nestedness of the assembling hedgerows, however, did not
asymptote within the eight years following restoration that the sites
were surveyed, so hedgerow networks may eventually reach sufficient
levels of nestedness to gain the robustness advantage.

@@

>>>>

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for system-level
  conservation biology. Using a long-term data set comprising nearly
  20,000 pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing assembly to be punctuated
  by significant reorganizations of interactions. In contrast, the
  non-assembling networks did not restructure as frequently. Across
  all communities, Pollinator species were opportunistic in the
  flowers they visited. Indeed, the most persistent and generalized
  species were also the most variable in their network positions. High
  species and interaction turnover was ubiquitous across assembling
  and non-assembling communities, though unique interactions turnover
  at higher rates in assembling hedgerows as the networks continually
  reorganize. Nestedness of assembling networks also increased through
  time, but there was no increase in robustness to simulated plant
  extinctions. The sensitivity of networks to cascading
  perturbations, however, increased as the communities assembled, at
  least partially due to accumulating species richness. We elucidate
  some of the mechanisms underlying plant-pollinator network assembly
  and restoration, while providing further evidence that hedgerows are
  a valuable tool for promoting species conservation and ecosystem
  provision in agricultural areas.
\end{abstract}

@@

%% there are other ways to assemble that are not preferentia;
%% attchment, particularly vis big reorganizations of interactions
%% Lauren I love this paragraph!
In contrast to the network build-up described by preferential
attachment, significant reorganizations of interactions can punctuate
assembly \citep{peel2014detecting}. Such significant reorganizations
of interactions, or network changing points, are observed in social
networks responding to abrupt shifts in the behavior of interactors
\citep{peel2014detecting}. In ecological communities, such shifts may
occur if, as new species colonize, resident species change their
interaction partners to optimize their foraging effort. In
plant-pollinator communities, theory predicts pollinators optimize
their use of floral resources to reduce interspecific competition and
improve resource-use efficiency \citep{pyke1984optimal,
  valdovinos2010consequences, valdovinos2013adaptive,
  albrecht2010plant, Bluthgen2007}. No studies, however, have examined
whether changing points occur during ecological network assembly, and
how these changes relate to the species behavior.

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially 'applied succession'
\citep[e.g.,][]{parker1997scale}. In pollination systems, the time
since an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, devoto2012understanding}, suggesting
interactions are changing as the community develops. Understanding the
mechanisms of network assembly will help to guide community
restoration. Facilitating network restoration is especially imperative
in areas where species interactions provide essential ecosystem
services, such as crop pollination. In intensively managed
agricultural landscapes, the demand for pollination services is the
greatest \citep{kremen-2008-10}. However, honey bees, managed
extensively around the world to provide crop pollination, are in
global decline \citep{neumann-2010-1, van-engelsdorp-2009-e6481}. In
addition, native pollinators, which are capable of providing
sufficient crop pollination \citep{kremen-2002-16816,
  winfree-2007-1105, kremen-2004-1109}, are in short supply because
these landscapes make poor habitats for pollinator populations
\citep{kremen-2002-16816}. To ensure the continued provision of
ecosystem services and curb biodiversity loss, it is critical to
restore pollinators and their interactions in agricultural
landscapes. To promote pollinator services in agriculture, farmers may
chose to plant strips of native plants along farm edges (hedgerows) to
help provide habitat for pollinators without removing arable land from
production. Hedgerows augment the richness, abundance and trait
diversity of pollinators in agricultural landscapes
\citep{morandin-2013-829, mgonigle-2015-x, kremen-2015-602,
  ponisio2015farm}. In addition, hedgerows promote the persistence and
colonization of floral resource specialists
\citep{mgonigle-2015-x}. It is important to further understand how
these new species are being incorporated into the network as the
community assembles, or the consequences for interaction patterns and
robustness.

%% Lauren I would put 10 year dataset; and I *loved* the way you
%% organized the ideas here!!
We explore the process of network development using a nine year
dataset of plant-pollinator communities assembly following hedgerow
restoration in the highly simplified and intensively managed
agricultural landscape of California's Central Valley.  We first
determine whether the mechanism underlying network assembly is a build
up of interactions as would be predicted by preferential attachment,
or punctuated by significant reorganizations of interactions (i.e.,
network changing points). Even with changing points in interaction
organization, networks could still be assembling via preferential
attachment if the network reorganizations were primarily driven the by
peripheral, temporally variable species while a stable, well-connected
core of species persist. We test whether the species that are most
variable in their network position --- and thus important contributors
to network reorganizations --- are less persistent and connected
species. To further explore the mechanisms underlying the temporal
dynamics of the networks, we examine patterns in the species and
interaction temporal turnover. Lastly, we investigate whether networks
are assembling toward predictable interaction patterns, and the
ramifications for the robustness of the networks to species extinction
and cascading perturbations.

@@

We surveyed plant-pollinator interaction networks of independent
assembling hedgerows communities (N=5), as well as in two types of
non-assembling communities to serve as controls: unrestored, weedy
field margins (N=19) and mature hedgerows (greater than 10 years since
planting, N=29). The sites were located in the Central Valley of
California in Yolo, Colusa and Solano Counties. This area is composed
of intensively managed agriculture --- primarily monocultures of
conventional row crops, vineyards and orchards. Hedgerows we planted
along field margins where they do not remove valuable land from
production. Plantings are between are ca.~3--6 m wide and
approximately 350 m long, bordering large (ca.\ 30--hectare) crop
fields. Hedgerows consist of native, perennial, shrub and tree
plantings including \textit{Rosa californica}, \textit{Cercis
  occidentalis}, \textit{Ceanothus spp.}, \textit{Heteromeles
  arbutifolia}, \textit{Sambucus mexicana}, \textit{Eriogonum spp.},
\textit{Baccharis spp.}, \textit{Salvia spp}. and others
\citep[Fig.~S1][]{menz-2010-4, kremen-2015-602, mgonigle-2015-x}. The
mean distance between monitoring sites was $15$ km, and the minimum
distance between sites of the same type sampled in the same year was 2
km.  The entire area surveyed spanned almost $300$ km$^2$. The crop
fields adjacent to all sites were similarly managed as intensive,
high-input monoculture.

@@

We calculate species persistence as the proportion of surveys in which
a plant or pollinator is observed. Species observed consistently
within and between years are thus maximally persistent. Weighted
species degree is calculated from interaction observations from an
extensive dataset from Yolo County (approx.~18000 interaction records)
that included both the data included in this study and additional data
from sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness centrality \citep{freeman1978centrality} at each
site through time. Closeness centrality describes the centrality of a
species in the network by calculating path lengths to other vertices
(species) in the graph \citep{freeman1978centrality}. The shorter the
mean path length to other species, the higher is the closeness
centrality. We use linear mixed models to test whether the species
closeness variability (log) is related to the persistence or degree of
that species \citep{lme4, lmetest}. We included random effects for
species, as well as site. Because the degree and persistence of
pollinators were strongly correlated, ($\rho = 0.84$, $p$-value $<$
$2*10^{-16}$), we include each explanatory variable in the model
separately. Plant degree and persistence were not significantly
correlated, but we use the same models as we did for the pollinators
for consistency. An approximately logarithmic increase in closeness
centrality, as would be expected with assembly by preferential
attachment, would also lead to a high variability in closeness scores,
so we test whether log closeness centrality increases through time.

@@

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, occupying the same network position and interacting with
similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species
(Fig.~\ref{fig:methods}). We develop a method to examine the temporal
turnover of interactions with weightings based on their similarity. We
followed \cite{ahn2010link} algorithm to hierarchically cluster all
the interactions (edges) across sites and years based on their
similarity, and build a dendrogram. The interaction similarity is
based how may plants and pollinators (vertices) two edges share
\citep{ahn2010link, kalinka2011linkcomm}. The more species edges
shared in common, the shorter the branch length between them on the
dendrogram.  We next calculated the temporal turnover of interactions
weighted by their similarity, as approximated by ``phylogenetic''
distance \citep{graham2008phylogenetic, picante-2010-1463}. When then
use linear models to test whether the weighted turnover of
interactions varied between assembling and non-assembling networks
\citep{lme4, lmetest}.

@@

To evaluate network nestedness, we used the estimator weighted NODF
\citep{almeida-neto-2008-1227}. NODF evaluates whether species with
fewer partners interact with subsets of partners with which more
connected species interact \citep{almeida-neto-2008-1227}. To estimate
modularity, we use a hierarchical clustering algorithm
\citep{Newman2004, csardi-2006}. We evaluate network specialization with
the metric H2, which estimates the deviation of the observed
interaction frequency between plants and pollinators from a null
expectation where all partners interact in proportion to their
abundances \citep{bluthgen-2006-9}. It ranges from zero for
generalized networks to one for specialized networks.  We calculated
standardized $z$-scores so that nestedness, modularity and
specialization metrics could be compared across communities. The
$z$-scores were calculated by generating an ensemble of $999$ randomly
assembled communities, subtracting the mean of the statistic
calculated across these communities from the observed value, and then
dividing by the standard deviation. To assemble random communities, we
reshuffled the interactions between species but fixed the total number
of interactions, species and interaction frequency distributions
\citep{Galeano2009}.

@@

\subsection*{Network robustness}
Lastly, we test whether the changes in interaction patterns associated
with network assembly affect the robustness of the network to species
loss and cascading perturbations. Following \cite{Memmott2004}, we
simulate plant species extinction and the subsequent extinction
cascades of pollinator species. Because the reproduction of plant
species if facilitated by active restoration efforts, it is unlikely
the extinction of pollinator species would affect plant populations in
the hedgerows. However, plants ceasing to bloom, for example in
response to drought, will likely affect the pollinators that depend on
them. We eliminate plants species based on their degree or abundance,
and then calculate the number of pollinators that secondarily went
extinct. The area below the extinction curve is an estimate of network
robustness \citep{Memmott2004, bipartite}.

We also explored how the robustness to cascading perturbations changed
as community assembled, using algebraic connectivity --- the second
smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness
(Gaiarsa et al., submitted). Algebraic connectivity relates to how
difficult it is to turn a network into completely disconnected groups
of species \citep{costa2007characterization}, and has implications to
how integrated is the dynamics of the elements of the networks
\citep{gibert2013spatial}. The larger the algebraic connectivity, the
more robust a network is to cascading perturbations, and the easier it
is to break the community into isolated groups of species (Gaiarsa et
al., submitted).

@@

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
Network nestedness significantly increased with assembly
(Fig.~\ref{fig:baci}, estimate of the slope of nestedness through time
$\pm$ SE, $1.834 \pm 0.6142$, $p$-value=$0.022$). All of the networks
were significantly nested ($z$-scores $>$ 2,
Fig.~\ref{fig:baci}). Modularity decreased (Fig.~\ref{fig:baci}),
though the slope was not significantly different from zero (estimate
of the slope of modularity through time $\pm$ standard error of the
estimate, $-0.524$ $\pm$ $0.295$, $p$-value=$0.124$). In addition,
none of the networks were significantly modular ($z$-scores $<$ 2,
Fig.~\ref{fig:baci}). Connectance decreased as the community assembled
(Fig.~\ref{fig:baci}, estimate of the slope of connectance through
time $\pm$ standard error of the estimate, $-0.0434$ $\pm$ $0.0152$,
$p$-value=$0.03$). Specialization also decreased, though the slope was
only marginally significantly different from zero (estimate of the
slope of specialization through time $\pm$ SE, $-0.926$ $\pm$ $0.450$,
$p$-value=$0.078$). Most communities were more generalized than
expected when interactions were randomized (Fig.~\ref{fig:baci}).

Both plant and pollinator species richness increased through time
(Fig.~\ref{fig:baci}, estimate of the slope of richness through time
$\pm$ SE, pollinators: $0.193$ $\pm$ $0.0729$, $p$-value=$0.008$;
plants: $0.212$ $\pm$ $0.0653$, $p$-value=$0.001$). Unsurprisingly,
pollinator species are colonizing and persisting at the assembling
hedgerows. Plant species richness is based on the flowers actually
visited by pollinators and not the presence of a particular plant
species at a site. Thus, though some new plant species may establish
themselves in the hedgerows, the increase in plant richness in the
networks is likely due to plants attracting visitors, as they offer
better rewards.

\subsection*{Network robustness}
Assembly did not effect the robustness of the networks to species
extinction when species where removed incrementally by degree
(estimate of the slope of robustness through time $\pm$ SE, $6*10^{-5}
\pm 4*10^{-3}$, $p$-value=$0.987$) or abundance ($0.001 \pm 0.003$,
$p$-value=$0.65$). In contrast, the sensitivity of networks to
cascading perturbations, as measured by the algebraic connectivity of
the network, increased as the network assembled (Fig.~\ref{fig:rob},
estimate of the slope of sensitivity to cascading perturbations
through time $\pm$ SE, $0.6814 \pm 0.272$, $p$-value=$0.042$).

@@

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations, the so called changing
points. If these network reorganizations were a product of
environmental forces alone, we would expect to observe the same
changing points at the same periods, consistently across all
sites. However, network changing points in non-assembling communities
are less frequent, and there are few consistent trends in when change
points occurred across all sites. Several sites had network changing
points between years 2009 and 2011 (Fig.~\ref{fig:changePoints}). In
California, 2011 marked the beginning of a multi-year drought. The
assembling hedgerows were not sampled in 2010, so disentangling
whether the changing points are due to skipping a year of assembly or
the drought is not possible. Interestingly, most assembling hedgerows
did not undergo a significant interaction reorganization immediately
after a hedgerow was planted (i.e., the transition from weedy field
margin to hedgerow). This result is consistent with the finding that
in our study system, hedgerow restoration takes several years to have
an impact on the plant-pollinator communities (Kremen and M'Gonigle,
in prep).

In addition to finding multiple network organization changing points
during assembly, the way in which these reorganizations occur was
different from what is expected by preferential attachment. Based on a
preferential attachment process, we expect that the most persistent
and high degree species would remain stable in the network core during
assembly \citep{barabasi1999emergence}. Surprisingly, however, we
encountered the opposite pattern. For example, the four most
ubiquitous species in our study landscape --- \textit{Halictus
  ligatus}, \textit{Halictus tripartitus}, \textit{Lasioglossum
  (Dialictus) incompletum}, and \textit{Toxomerus marginatus} --- were
the only species that changed which module they were a member across
years in all the assembling hedgerows. Because species degree and
persistence were strongly correlated, it is difficult to disentangle
the causal mechanism for why species with those characteristics are so
variable in their network position. Generalized species may be able to
better exploit the limited floral resources in the intensively managed
agriculture landscape, and thus also be the most persistent \citep[in
ant-plant mutualisms, ][]{diaz2010changes}. More persistent species
usually have longer phenologies, so they can visit many different
flowers, resulting in a higher degree \citep{Vazquez2009,
  fort2016abundance}. Either way, our result suggests that adaptable
species can change their network position to utilize the most
advantageous floral resources available, which may depend on the other
pollinator species that are present, and the state of the plant
community \citep{macleod2016measuring, gomez2006ecological,
  waser1996generalization}. Thus given the opportunity and ability to
use different resources, species will often change their network
positions \citep{macleod2016measuring}.

@@

Interestingly, however, the changes in network patterns with assembly
the robustness of hedgerow communities to species loss did not change
with assembly. This is particularly surprising given the observed
increase in nestedness, which is often associated with an enhanced in
robustness to extinction \citep{Memmott2004}. Perhaps assembling
hedgerows have yet to reach sufficient levels of nestedness to realize
the benefits nestedness confers. Nestedness of the assembling
hedgerows, however, did not asymptote within the eight years following
restoration that the sites were surveyed, so hedgerow networks may
eventually reach sufficient levels of nestedness to gain the
robustness advantage.

Contrary to the general restoration goals, the susceptibility of the
networks to cascading perturbations increased as the communities
assembled. Because network vulnerability to cascading perturbations,
as measured by algebraic connectivity, is correlated with species
richness, the increase and plant and pollinator richness following
restoration is at least partially responsible for the increase to
cascading effects. Connectance is also positively related to algebraic
connectivity \citep{gibert2013spatial}, but because we observed a
decrease in connectance, topological characteristics of the networks
beyond species richness and connectance are needed to explain the
increased sensitivity to perturbations spreading. These hedgerows were
designed to provide floral resources to the largest number of
pollinators across the growing season \citep{menz-2010-4}. The
generalized nature of the floral community may explain why the
networks tended to be more generalized than expected if interactions
were randomly distributed across species (Fig.~\ref{fig:baci}). In
addition, the design of the hedgerow plantings may have facilitated
the emergence of a single, highly connected module in all of the
networks (see \ref{fig:changePoints2} for examples). This network
configuration results in short path lengths (the distance between
species in a network based on their shared partners), and thus, a
perturbation in one species can more easily spread to other
species. In order to promote more resilient communities, future
restoration efforts should explore designing floral communities to
promote more interaction partitioning using, for example, algorithms
to optimize different network properties based on prior knowledge of
pollinator floral preferences \citep{mgonigle2016tool}, and on desired
network architectures that renders them more robust both to species
loss and to cascading effects.

% The relationship between diversity and stability in networks
% has been the subject of considerable debate
% \citep[e.g.,][]{may1972will, pimm1984complexity,
%   montoya2006ecological}. Our results provide one of the few empirical
% examples of how restoring species diversity contributes to enhancing
% network stability.

% providing further evidence that hedgerows are a valuable tool for
% promoting species conservation and ecosystem provision in agricultural
% areas \citep{mgonigle-2015-x, ponisio2015farm,
%   kremen-2015-602}.

@@

\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{figures/scheme.pdf}
  \caption{Diagram illustrating the analysis to examine the temporal
    turnover of interactions weighted based on their similarity. A, B
    and C are animal species, and Ps are plant species. The dendrogram
    depicts the interaction similarity across years based on the
    number of shared constituent species.}
  \label{fig:methods}
\end{figure}
\clearpage
